Identification and performance of stock-recruitment functions in state

### 2024-02-08 Ecov_study/recruitment_functions/presentation/SRR_presentation.Rmd
final presentation?

# Sims
## Simulated Data Examples - Type 1
```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.height='40%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'recruit_ecov.pdf') )
```

@@

<!-- ```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.width='40%', fig.align='center'} -->
<!--  knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'om_57.59.61.63.121.123.125.127.185.187.189.191.249.251.253.255._Recr.plot.png') ) -->
<!-- ``` -->

@@

<!-- ```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.width='40%', fig.align='center'} -->
<!--  knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'om_57.59.61.63.121.123.125.127.185.187.189.191.249.251.253.255._SSB.png') ) -->
<!-- ``` -->

@@

```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.height='40%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 'reg_tree_AIC_best_beta_fix.pdf') )
```

```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.height='40%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix_384', 'reg_tree_AIC_best_beta_fix_384.pdf') )
```

## Recommendations for future research
- Additional fishing histories, including some that include years with F < $F_{MSY}$
- Recruitment random effect trends
- Ecov models with trends or AR(2) dynamics
- Multivariate ecov processes
- Ecov processes affecting multiple stock parameters, or multiple Ecov processes affecting recruitment (simultaneous or sequential)

>>>>

# Sims
## Simulated Data Examples - Ecov and SRR 
```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.height='40%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'recruit_ecov.pdf') )
```

@@

@@

## Simulated Data Examples - Catch Timeseries
```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.width='90%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'Catch_sims.png') )
```

@@

```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.height='35%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 'reg_tree_AIC_best_beta_fix.pdf') )
```

```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.height='35%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix_384', 'reg_tree_AIC_best_beta_fix_384.pdf') )
```

## Recommendations for future research
- Additional fishing histories, including some that include years with F < $F_{MSY}$
- Recruitment random effect trends
- Ecov models with stronger effects, trends, or AR(2) dynamics
- Multivariate ecov processes
- Ecov processes affecting multiple stock parameters, or multiple Ecov processes affecting recruitment (simultaneous or sequential)
